### 2016-08-15 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex

\subsubsection{Leakage}
An air leakage measurement system was used to measure the amount of leakage associated with each structure. The amount of leakage in the East Structure was measured as 0.024~m$^2$. For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed and as 0.054~m$^2$ when the stairway door was opened.

@@

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\subsection{Tests~24 \& 25}
Similar to Tests~22 and 23, Tests~24 and 25 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure. Also, the stairwell door was unable to completely close. So, when it was in the ``closed'' position at the beginning of the tests, there was a 152~mm (6~in) gap between the door and its frame.

>>>>

\subsubsection{Leakage}
An air leakage measurement system was used to measure the amount of leakage associated with each structure. The amount of leakage in the East Structure was measured as 0.024~m$^2$. For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) during Tests~24 and 25.

@@

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed a nearly identical procedure to change the ventilation. The starting configuration for Test~22 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~23 had the same door in the closed position. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\subsection{Tests~24 \& 25}
Similar to Tests~22 and 23, Tests~24 and 25 followed a nearly identical test procedure. The starting configuration for Test~24 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~25 had the same door in the closed position. Also, the stairwell door was unable to completely close. When it was in the ``closed'' position at the beginning of each test, there was a 152~mm (6~in) gap between the door and its frame. Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.
